Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-06-07 PAPER.tex
Straightened out index and summation notation

We are interested in estimating the three-dimensional power spectrum of the EoR.  
Visibilities are measurements of the Fourier transform of the sky along two spatial dimensions (using the flat-sky approximation), and since we are interested in three-dimensional Fourier modes we only need to take one Fourier transform of our visibilities along the line-of-sight dimension.  We consider band powers $p_\alpha$ of the power spectrum of $\textbf{x}$ over some range in cosmological $\mathbf{k}$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes).  The fundamental dependence of the covariance on the power spectrum band powers $p_\alpha$ is encoded as 
% JEA - Should distinguish slightly more clearly between Q and dC/dp_alpha
\begin{equation}
\textbf{S} = \sum_\alpha p_\alpha \frac{\partial\textbf{C}}{\partial p_\alpha} \equiv \sum_\alpha p_\alpha \textbf{Q}_\alpha
%\textbf{S} = p_{\alpha} \frac{\partial\textbf{C}}{\partial p_{\alpha}}
%\frac{\partial\textbf{C}}{\partial p_{\alpha}} \equiv \textbf{Q}^{\alpha}
\end{equation}
where we define $\frac{\partial\textbf{C}}{\partial p_\alpha} \equiv \textbf{Q}_{\alpha}$.
% JEA - ah, the dimensions again
% which has dimensions ($N_{f}$,$N_{f}$).

The optimal quadratic estimator prescription is then to compute
\begin{equation}
\label{eq:OQE}
\widehat{p}_{\alpha}  =  ({\F^{-1}})_\alpha^{\beta} (\widehat{q}_{\beta} - \widehat{b}_{\beta} )
\end{equation}
where $\F$ is the Fisher matrix 
\begin{equation}
F^{\alpha \beta} \equiv \frac{1}{2} \textrm{tr} \left( \C^{-1} \textbf{Q}^{\alpha} \C^{-1} \textbf{Q}^{\beta} \right)
\end{equation}
and
\begin{equation}
\label{eq:OQEQuadratic}
\widehat{q}_\alpha =  \half \textbf{x}^\dagger \invC \textbf{Q}^{\alpha}  \invC \textbf{x} 
\end{equation}
and
\begin{equation}
\label{eq:OQELinear}
\widehat{b}_{\alpha} = \half \Tr\left( \mathbf{U} \invC \textbf{Q}^{\alpha} \invC \right).
\end{equation}
This estimator is the minimum variance (smallest error bar) estimate of the power spectrum  subject to the constraint that it is also unbiased; that is, the ensemble average of the estimator is equal to its true value
\begin{equation}
\label{eq:super_unbiased}
\langle \widehat{p}_{\alpha} \rangle = p_\alpha.
\end{equation}
\citep{tegmark_et_al1997a,bond_et_al1998}

@@

%We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
Motivated by the desire to retain the advantageous behavior of suppressing contributions of $\mathbf{U}$ to estimates of the EoR power spectrum, we note that is possible to define a modified version of the quadratic estimator 
%which may still produce an unbiased estimate, 
where Equation \eqref{eq:OQEQuadratic} is replaced by
\begin{equation}
\label{eq:qhat}
\widehat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}
\end{equation}
where $\textbf{R}$ is a weighting matrix chosen by the data analyst.  For example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $\textbf{R} \equiv \textbf{I}$, the identity matrix.
The matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum parameters $\partial \C/\partial p_\alpha$ but in practice also does other things, including implementing a transform of the frequency-domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
%with dimensions ($N_{f}$,$N_{f}$) --- as

%%% COME BACK HERE
% Need to still explain the motivation for this
With an appropriate normalization matrix $\textbf{M}$, the quantity
%We normalize our power spectrum estimates using the matrix $\textbf{M}$:
\begin{equation}
\label{eq:phat}
\widehat{\textbf{P}} = \textbf{M}\widehat{\textbf{q}}
\end{equation}
is a sensible estimate of the true power spectrum $\textbf{P}$. To ensure that $\textbf{M}$ correctly normalizes our power spectrum, one may take the expectation value of Equation \eqref{eq:phat} to obtain
\begin{eqnarray}
\langle \widehat{P}_\alpha \rangle &=& \frac{1}{2} \sum_{\beta \gamma} M_{\alpha \gamma}  \textrm{tr} \left( \textbf{R}\textbf{Q}^{\gamma}\textbf{R} \textbf{Q}^{\beta}\right) p_\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right) \nonumber \\
&\equiv & \sum_{\beta} W_{\alpha \beta} p_\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right), \label{eq:Wpplusbias}
\end{eqnarray}
where $W_{\alpha \beta}$ are elements of a window function matrix. Let's consider the first term of this expression (again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit). If $\mathbf{W}$ ends up being the identity matrix for our choices of $\mathbf{R}$ and $\mathbf{M}$, then we recover Equation \eqref{eq:super_unbiased} for the first term, and we have an estimator that has no multiplicative matrix bias. However, Equation \eqref{eq:super_unbiased} is a rather restrictive condition, and it is possible to violate it and still have a sensible (and correctly normalized) power spectrum estimate. In particular, as long as the rows of $\mathbf{W}$ sum to unity, our power spectrum will be correctly normalized. Beyond this, the data analyst has a choice for $
\textbf{M}$. For simplicity in this section we choose $\textbf{M}$ to be diagonal, although we discuss other cases for the analysis 
of PAPER-64 data as explained in Section \ref{sec:Bias}. In a preview of what is to come, we also stress that the derivation that leads to Equation \eqref{eq:Wpplusbias} assumes that $\mathbf{R}$ and $\mathbf{x}$ are not correlated. If this assumption is violated, a simple application of the (now incorrect) formulae in this section can result in an improperly normalized power spectrum estimator that does not conserve power, i.e., one that has signal loss.
% JEA - is one really free to choose M and R independently?

@@

\begin{equation}
\label{eq:Pin}
\widehat{P}_{\rm in,\alpha} \equiv \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
\end{equation}

@@

\begin{eqnarray}
\label{eq:sigloss}
\widehat{P}_{\rm out,\alpha} &\equiv& \widehat{\textbf{P}}_{r,\alpha} \nonumber\\%-\widehat{\textbf{P}}_{x,\alpha} \nonumber \\
&=& \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r},% - \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x},
\end{eqnarray}
where, for illustrative purposes and notational simplicity, we have written these equations with scalar normalizations M, even though for our numerical results we choose a diagonal matrix normalization using $\mathbf{M}$ as in Equation \eqref{eq:phat}.

@@

\begin{eqnarray}
\label{eq:crossterm_full}
\widehat{P}_{\rm out,\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) \nonumber \\%- 
%\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
&=& \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
&+& \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \text{M}^{\alpha}_{d}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} %\nonumber \\
%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
\end{eqnarray}
Assuming \textbf{R}$_{r}$ is symmetric, the two cross-terms (terms with one copy of $\textbf{e}$ and one copy of $\textbf{x}$) can be summed together as:

\begin{eqnarray}
\label{eq:crossterm}
\widehat{P}_{\rm out,\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
&+& 2 \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} %\nonumber \\
%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
\end{eqnarray}
In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: empirically estimated inverse covariance weighting ($\textbf{R}_{r} \equiv \widehat{\textbf{C}}_{r}^{-1}$) and uniform weighting ($\textbf{R}_{r} \equiv \textbf{I}$). We will now examine the behavior of this equation in three different regimes of the injected signal - very weak (left ends of the $P_{\rm in}$ axes in Figure \ref{fig:sigloss_terms}), very strong (right ends), and in between (middle portions).

@@

\begin{eqnarray}
\widehat{P}_{\rm in,\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
\widehat{P}_{\rm out,\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r}.% \nonumber \\
%&&\phantom{=====} 
%-  \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\widehat{\textbf{C}}_{x}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{x}^{-1}\textbf{x}. 
\end{eqnarray}

@@

Tailoring window functions is one way to suppress foreground biases (similar discussions to the following one are in \citet{liu_et_al2014b} and \citetalias{ali_et_al2015}). As alluded to in Section \ref{sec:SiglossOverview}, we 
have a choice for the normalization matrix $\textbf{M}$ in Equation \eqref{eq:phat}. For the analysis of PAPER-64 data, we 
compute $\textbf{M}$ using the matrix $\textbf{F}$ (chosen because this would be the Fisher matrix if $\textbf{R} \equiv \textbf{C}^{-1}$), defined as:

\begin{equation}
\textbf{F}_{\alpha\beta} = \frac{1}{2} \text{tr} [\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{Q}^{\beta} ]
\end{equation}

\noindent where $\textbf{R}$ is the data-weighting matrix and $\alpha$ and $\beta$ are wavebands in $k_{\parallel}$. We take 
the Cholesky decomposition of $\textbf{F}$, decomposing it into two lower triangular matrices (which is possible since $\textbf{F}$ is Hermitian):

\begin{equation}
\textbf{F} = \textbf{LL}^{\dagger}.
\end{equation}

@@

\noindent where $\textbf{D}$ is a diagonal matrix. In doing so, our window function, defined as $\textbf{W} = \textbf{MF}$, 
becomes:

@@

\noindent Because of the nature of the lower triangular matrix, this window function has the property of preventing the leakage 
of foreground power from low-$k$ to high-$k$ modes. Specifically, we order the elements in $\textbf{F}$ in such a way so that 
power can leak from high-$k$ modes to low-$k$ modes, but not vice versa. Since most foreground power shows up at low-$k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing the 
contamination of foreground bias. This tailored window function was used in the \citetalias{ali_et_al2015} analysis, however throughout this paper, we use a diagonal $\textbf{M}$ for simplicity.

>>>>

We are interested in estimating the three-dimensional power spectrum of the EoR.  
Visibilities are measurements of the Fourier transform of the sky along two spatial dimensions (using the flat-sky approximation), and since we are interested in three-dimensional Fourier modes we only need to take one Fourier transform of our visibilities along the line-of-sight dimension.  We consider band powers $p_\alpha$ of the power spectrum of $\textbf{x}$ over some range in cosmological $\mathbf{k}$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes).  The fundamental dependence of the covariance on the power spectrum band powers $p_\alpha$ is encoded as 
% JEA - Should distinguish slightly more clearly between Q and dC/dp_alpha
\begin{equation}
\textbf{S} = \sum_\alpha p^\alpha \frac{\partial\textbf{C}}{\partial p^\alpha} \equiv \sum_\alpha p^\alpha \textbf{Q}^\alpha
%\textbf{S} = p_{\alpha} \frac{\partial\textbf{C}}{\partial p_{\alpha}}
%\frac{\partial\textbf{C}}{\partial p_{\alpha}} \equiv \textbf{Q}^{\alpha}
\end{equation}
where we define $\frac{\partial\textbf{C}}{\partial p_\alpha} \equiv \textbf{Q}_{\alpha}$.
% JEA - ah, the dimensions again
% which has dimensions ($N_{f}$,$N_{f}$).

The optimal quadratic estimator prescription is then to compute
\begin{equation}
\label{eq:OQE}
\widehat{p}^{\alpha}  = \sum_\beta ({\F^{-1}})^{\alpha\beta} (\widehat{q}^{\beta} - \widehat{b}^{\beta} )
\end{equation}
where $\F$ is the Fisher matrix 
\begin{equation}
F^{\alpha \beta} \equiv \frac{1}{2} \textrm{tr} \left( \C^{-1} \textbf{Q}^{\alpha} \C^{-1} \textbf{Q}^{\beta} \right)
\end{equation}
and
\begin{equation}
\label{eq:OQEQuadratic}
\widehat{q}^\alpha =  \half \textbf{x}^\dagger \invC \textbf{Q}^{\alpha}  \invC \textbf{x} 
\end{equation}
and
\begin{equation}
\label{eq:OQELinear}
\widehat{b}^{\alpha} = \half \Tr\left( \mathbf{U} \invC \textbf{Q}^{\alpha} \invC \right).
\end{equation}
This estimator is the minimum variance (smallest error bar) estimate of the power spectrum  subject to the constraint that it is also unbiased; that is, the ensemble average of the estimator is equal to its true value
\begin{equation}
\label{eq:super_unbiased}
\langle \widehat{p}^{\alpha} \rangle = p^\alpha.
\end{equation}
\citep{tegmark_et_al1997a,bond_et_al1998}

@@

%We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
Motivated by the desire to retain the advantageous behavior of suppressing contributions of $\mathbf{U}$ to estimates of the EoR power spectrum, we note that is possible to define a modified version of the quadratic estimator 
%which may still produce an unbiased estimate, 
where Equation \eqref{eq:OQEQuadratic} is replaced by
\begin{equation}
\label{eq:qhat}
\widehat{q}^{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}
\end{equation}
where $\textbf{R}$ is a weighting matrix chosen by the data analyst.  For example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $\textbf{R} \equiv \textbf{I}$, the identity matrix.
The matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum parameters $\partial \C/\partial p^\alpha$ but in practice also does other things, including implementing a transform of the frequency-domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
%with dimensions ($N_{f}$,$N_{f}$) --- as

%%% COME BACK HERE
% Need to still explain the motivation for this
With an appropriate normalization matrix $\textbf{M}$, the quantity
%We normalize our power spectrum estimates using the matrix $\textbf{M}$:
\begin{equation}
\label{eq:phat}
\widehat{\textbf{P}} = \textbf{M}\widehat{\textbf{q}}
\end{equation}
is a sensible estimate of the true power spectrum $\textbf{P}$. To ensure that $\textbf{M}$ correctly normalizes our power spectrum, one may take the expectation value of Equation \eqref{eq:phat} to obtain
\begin{eqnarray}
\langle \widehat{P}^\alpha \rangle &=& \frac{1}{2} \sum_{\beta \gamma} M^{\alpha \gamma}  \textrm{tr} \left( \textbf{R}\textbf{Q}^{\gamma}\textbf{R} \textbf{Q}^{\beta}\right) p^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right) \nonumber \\
&\equiv & \sum_{\beta} W^{\alpha \beta} p^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right), \label{eq:Wpplusbias}
\end{eqnarray}
where $W^{\alpha \beta}$ are elements of a window function matrix. Let's consider the first term of this expression (again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit). If $\mathbf{W}$ ends up being the identity matrix for our choices of $\mathbf{R}$ and $\mathbf{M}$, then we recover Equation \eqref{eq:super_unbiased} for the first term, and we have an estimator that has no multiplicative matrix bias. However, Equation \eqref{eq:super_unbiased} is a rather restrictive condition, and it is possible to violate it and still have a sensible (and correctly normalized) power spectrum estimate. In particular, as long as the rows of $\mathbf{W}$ sum to unity, our power spectrum will be correctly normalized. Beyond this, the data analyst has a choice for $
\textbf{M}$. For simplicity in this section we choose $\textbf{M}$ to be diagonal, although we discuss other cases for the analysis 
of PAPER-64 data as explained in Section \ref{sec:Bias}. In a preview of what is to come, we also stress that the derivation that leads to Equation \eqref{eq:Wpplusbias} assumes that $\mathbf{R}$ and $\mathbf{x}$ are not correlated. If this assumption is violated, a simple application of the (now incorrect) formulae in this section can result in an improperly normalized power spectrum estimator that does not conserve power, i.e., one that has signal loss.
% JEA - is one really free to choose M and R independently?

@@

\begin{equation}
\label{eq:Pin}
\widehat{P}_{\rm in}^{\alpha} \equiv \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
\end{equation}

@@

\begin{eqnarray}
\label{eq:sigloss}
\widehat{P}_{\rm out}^{\alpha} &\equiv& \widehat{\textbf{P}}_{r}^{\alpha} \nonumber\\%-\widehat{\textbf{P}}_{x,\alpha} \nonumber \\
&=& \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r},% - \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x},
\end{eqnarray}
where, for illustrative purposes and notational simplicity, we have written these equations with scalar normalizations M, even though for our numerical results we choose a diagonal matrix normalization using $\mathbf{M}$ as in Equation \eqref{eq:phat}.

@@

\begin{eqnarray}
\label{eq:crossterm_full}
\widehat{P}_{\rm out}^{\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) \nonumber \\%- 
%\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
&=& \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
&+& \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \text{M}^{\alpha}_{d}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} %\nonumber \\
%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
\end{eqnarray}
Assuming \textbf{R}$_{r}$ is symmetric, the two cross-terms (terms with one copy of $\textbf{e}$ and one copy of $\textbf{x}$) can be summed together as:

\begin{eqnarray}
\label{eq:crossterm}
\widehat{P}_{\rm out}^{\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
&+& 2 \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} %\nonumber \\
%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
\end{eqnarray}
In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: empirically estimated inverse covariance weighting ($\textbf{R}_{r} \equiv \widehat{\textbf{C}}_{r}^{-1}$) and uniform weighting ($\textbf{R}_{r} \equiv \textbf{I}$). We will now examine the behavior of this equation in three different regimes of the injected signal - very weak (left ends of the $P_{\rm in}$ axes in Figure \ref{fig:sigloss_terms}), very strong (right ends), and in between (middle portions).

@@

\begin{eqnarray}
\widehat{P}_{\rm in}^{\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
\widehat{P}_{\rm out}^{\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r}.% \nonumber \\
%&&\phantom{=====} 
%-  \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\widehat{\textbf{C}}_{x}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{x}^{-1}\textbf{x}. 
\end{eqnarray}

@@

Tailoring window functions is one way to suppress foreground biases (similar discussions to the following one are in \citet{liu_et_al2014b} and \citetalias{ali_et_al2015}). As alluded to in Section \ref{sec:SiglossOverview}, we 
have a choice for the normalization matrix $\textbf{M}$ in Equation \eqref{eq:phat}. For the analysis of PAPER-64 data, we 
compute $\textbf{M}$ using the matrix $\textbf{G}$ (which would be the Fisher matrix if $\textbf{R} \equiv \textbf{C}^{-1}$), defined as:

\begin{equation}
\textbf{G}^{\alpha\beta} = \frac{1}{2} \text{tr} [\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{Q}^{\beta} ]
\end{equation}

\noindent where $\textbf{R}$ is the data-weighting matrix and $\alpha$ and $\beta$ are wavebands in $k_{\parallel}$. We take 
the Cholesky decomposition of $\textbf{G}$, decomposing it into two lower triangular matrices (which is possible since $\textbf{G}$ is Hermitian):

\begin{equation}
\textbf{G} = \textbf{LL}^{\dagger}.
\end{equation}

@@

\noindent where $\textbf{D}$ is a diagonal matrix. In doing so, our window function, defined as $\textbf{W} = \textbf{MG}$ (see Equation \eqref{eq:Wpplusbias}), 
becomes

@@

\noindent Because of the nature of the lower triangular matrix, this window function has the property of preventing the leakage 
of foreground power from low-$k$ to high-$k$ modes. Specifically, we order the elements in $\textbf{G}$ in such a way so that 
power can leak from high-$k$ modes to low-$k$ modes, but not vice versa. Since most foreground power shows up at low-$k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing the 
contamination of foreground bias. This tailored window function was used in the \citetalias{ali_et_al2015} analysis, however throughout this paper, we use a diagonal $\textbf{M}$ for simplicity.
